Recent Advances in Reliable Transport Protocols\footnote{ Parts of the text in this chapter have appeared in the following publications by the same author(s): \cite{login}, \cite{mptcp-cc}, \cite{raiciu2012hard}, ~\cite{nowlan12fitting} and~\cite{iyengar10minion}.}

### 2013-07-25 Compiled/chapter5/internet.tex
bibliography chapter 5 with most hyperlinks

A second, and widely deployed middlebox, is the Network Address Translator (NAT). The NAT was defined in \cite{rfc1631} and various extensions have been developed over the years. One of the initial motivation for NAT was to preserve public IP addresses and allow a group of users to share a single IP address. This enabled the deployment of many networks that use so-called \emph{private addresses} \cite{rfc1918} internally and rely on NATs to reach the global Internet. At some point, it was expected that the deployment of IPv6 would render NAT obsolete. This never happened and IPv6 deployment is still very slow \cite{Dhamdhere_IPv6:2012}. Furthermore, some network administrators have perceived several benefits with the deployment of NATs \cite{rfc2993} including : reducing the exposure of addresses, topology hiding, independence from providers, \ldots Some of these perceived advantages have caused the IETF to consider NAT for IPv6 as well, despite the available address space. Furthermore, the IETF, vendors and operators are considering the deployment of large scale Carrier Grade NATs (CGN) to continue to use IPv4 despite the depletion of the addressing space \cite{Perreault_CGN:2012} and also to ease the deployment of IPv6 \cite{rfc6264}. NATs will remain a key element of the deployed networks for the foreseeable future.

@@

Firewalls are equally widespread in the Internet, being deployed by most cellular operators \cite{netpiculet}. Home routers often act as
firewalls, blocking new protocols and even existing ones (e.g. UDP) \cite{nat-study}. Most servers also deploy firewalls to restrict
in-bound traffic \cite{sherry2012making}. Additionally, many modern operating systems come with ``default-on'' firewalls. For instance, 
the Windows 7 firewall explicitly asks users to allow incoming connections and to whitelist applications allowed to make outgoing 
connections.

>>>>

A second, and widely deployed middlebox, is the Network Address Translator (NAT). The NAT was defined in \cite{rfc1631} and various extensions have been developed over the years. One of the initial motivation for NAT was to preserve public IP addresses and allow a group of users to share a single IP address. This enabled the deployment of many networks that use so-called \emph{private addresses} \cite{rfc1918} internally and rely on NATs to reach the global Internet. At some point, it was expected that the deployment of IPv6 would render NAT obsolete. This never happened and IPv6 deployment is still very slow \cite{Dhamdhere_IPv6:2012}. Furthermore, some network administrators have perceived several benefits with the deployment of NATs \cite{rfc2993} including : reducing the exposure of addresses, topology hiding, independence from providers, \ldots Some of these perceived advantages have caused the IETF to consider NAT for IPv6 as well, despite the available address space. Furthermore, the IETF, vendors and operators are considering the deployment of large scale Carrier Grade NATs (CGN) to continue to use IPv4 despite the depletion of the addressing space \cite{rfc6888} and also to ease the deployment of IPv6 \cite{rfc6264}. NATs will remain a key element of the deployed networks for the foreseeable future.

@@

Firewalls are equally widespread in the Internet, being deployed by most cellular operators \cite{wang2011untol}. Home routers often act as
firewalls, blocking new protocols and even existing ones (e.g. UDP) \cite{nat-study}. Most servers also deploy firewalls to restrict
in-bound traffic \cite{sherry2012making}. Additionally, many modern operating systems come with ``default-on'' firewalls. For instance, 
the Windows 7 firewall explicitly asks users to allow incoming connections and to whitelist applications allowed to make outgoing 
connections.
